% TeX_root = ./joel_sleeba.tex
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
% \usepackage{soul}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\renewcommand{\familydefault}{\sfdefault}
% \definecolor{hanblue}{rgb}{0.32, 0.32, 0.65}
\definecolor{hanblue}{rgb}{0.55, 0.20, 0.22}

\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=hanblue,
  pdftitle={Overleaf Example},
  pdfpagemode=FullScreen,
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries \color{hanblue}
}{}{0em}{}[\color{hanblue}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
\item\small{
    {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.0in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} &
% Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} &
% Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge Joel Sleeba} \\ \vspace{5pt}
  % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
  % \small \raisebox{-0.1\height}\faPhone\ 123-456-7890 ~
  % \href{mailto:joelsleeba1@gmail.com}{\raisebox{-0.2\height}\faEnvelope\
  % \ul{email@gmail.com}} ~
  \small
  \href{mailto:joelsleeba1@gmail.com}{\raisebox{-0.2\height}\faEnvelope\
  {joelsleeba1@gmail.com}} ~
  \href{https://twitter.com/JoelSleeba/}{\raisebox{-0.2\height}\faTwitter\ {JoelSleeba}}
  ~
  \href{https://github.com/joelsleeba}{\raisebox{-0.2\height}\faGithub\ {joelsleeba}}
  ~
  \href{https://joelsleeba.github.io/}{\raisebox{-0.2\height}\faGlobe\ {joelsleeba.github.io}}

  \vspace{-5pt}
\end{center}

% \section{About Me}
% I am a math graduate from IISER Thiruvananthapuram. I am broadly
% interested in operator algebras. Beside math I am interested in
% Linux, open source software, photography and movies.
% \vspace{-5pt}

% \section{Research Interests}
% I am broadly interested in {\bf functional analysis} and {\bf
% harmonic analysis}. I am currently working on {\bf operator
% algebras}. As part of my master's thesis I have worked on {\bf
% Fourier analysis}.
% \vspace{-5pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{PhD in Mathematics}{August 2024 -- Present}
{University of Houston | GPA: 4.0/4.0}{Houston, TX}
\resumeItemListStart
% \resumeItem{GPA: 8.38 (out of 10)}
\resumeItem{Relevant coursework: measure theory, functional analysis}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-12pt}

\resumeSubHeadingListStart
\resumeSubheading
{Master of Science in Mathematics}{October 2021 -- May 2023}
{Indian Institute of Science Education and Research | GPA:
8.38/10.0}{Thiruvananthapuram, Kerala}
\resumeItemListStart
% \resumeItem{GPA: 8.38 (out of 10)}
\resumeItem{Relevant coursework: linear algebra, functional analysis,
topology, measure theory, probability theory, machine learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-12pt}

\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Science in Mathematics}{June 2018 -- May 2021}
{Madras Christian College | GPA: 8.04/10.0}{Chennai, Tamil Nadu}
\resumeItemListStart
% \resumeItem{GPA: 8.01 (out of 10)}
\resumeItem{Relevant coursework: linear algebra, real analysis,
complex analysis, abstract algebra}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8pt}

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item \small Functional Analysis
%                 \item Measure Theory
%                 \item Probability Theory
%                 \item Representation Theory
%                 \item Finite Frames
%                 \item Topology
%                 \item Real Analysis
%                 \item Machine Learning
%
%             \end{itemize}
%         \end{multicols}
%         \vspace*{0.0\multicolsep}
%     %\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Research Experience}
\resumeSubHeadingListStart
% \href{https://scholar.google.co.in/citations?hl=en\&user=8Wvnt8MAAAAJ\&view_op=list_works\&sortby=pubdate}{Prof.
% M N N Namboodiri},
\resumeSubheading
{Peaking Qubit Channels}{October 2023 -- April 2024}
{Research
Project}{\href{https://iqac.cusat.ac.in/Web/profile_view/433/Dr.SHANKARP}{Dr.
P Shankar}, Cochin University of Science and Technology (CUSAT)}
\resumeItemListStart
\resumeItem{Exploring the possibility to introduce the notion of
classical peak points to unital qubit channels.}
\resumeItem{Tried to employ the characterisation of unital qubit
  channels from \textit{\href{https://arxiv.org/abs/2301.01358}{On
unital qubit channels}}, Li and Choi}
\resumeItem{Learned about completely positive maps, Choi's theorem,
and Steinspring dilation theorem.}
\resumeItem{References: \textit{Completely Bounded Maps and Operator
  Algebras}, Vern Paulsen and \textit{Completely Positive Maps on
Complex Matrices}, Man-Duen Choi}
\resumeItemListEnd

% \resumeSubheading
%   {Unitary Invariants for Representations of Operator
% Algebras}{Sept. 2023 -- Present}
%   {Reading
% Project}{\href{https://www.isibang.ac.in/~soumyashant/}{Dr.
% Soumyashant Nayak}, ISI Bangalore}
%   \resumeItemListStart
%     \resumeItem{Plans to review the article of the same title by
% Richard Kadison.}
%     \resumeItem{Reviewed representations of finite groups and C*
% algebras as the initial stage of the reading project.}
%   \resumeItemListEnd

\resumeSubheading
{Introduction to C* Algebras}{June 2023 -- Sept. 2023}
{Summer Reading
Project}{\href{https://iqac.cusat.ac.in/Web/profile_view/433/Dr.SHANKARP}{Dr.
P Shankar}, CUSAT}
\resumeItemListStart
\resumeItem{Learned the basics of Banach and C* algebras, Gelfand
transforms, functional calculus, sesquilinear forms, GNS constructions.}
\resumeItem{References: \textit{C* Algebras and Operator Theory} by
Gerard Murphy and \textit{An Invitation to C* Algebras} by William Arveson.}
% \resumeItem{This project motivated me to further explore C*
% algebras and their representations.}
\resumeItemListEnd

\resumeSubheading
{A Study in Fourier Analysis}{January 2023 -- May 2023}
{Masters
Thesis}{\href{https://www.iisertvm.ac.in/faculty/devarajp}{Dr. P
Devaraj}, IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{Learned about Fourier transforms in the circle and line,
  $\ell^p$ convergence of Fourier series, Fourier Inversion, and
classical Paley Wiener theorems}
\resumeItem{References: \textit{Early Fourier Analysis} by Hugh L
Montgomery and \textit{Real and Complex Analysis} by Walter Rudin.}
\resumeItem{\href{https://github.com/joelsleeba/Master-s-Project/blob/master/Thesis/main.pdf}{Read
my report on GitHub}}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROJECTS-----------
\section{Workshops}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Mathematics Training and Talent Search (MTTS)} $|$
\emph{Level 1 Summer Camp}}{April 2021 -- May 2021}
\resumeItemListStart
\resumeItem{Participated in the online summer camp hosted by MTTS
trust, funded by the National Board of Higher Mathematics.}
\resumeItem{Helped revise concepts in group theory, real analysis and
linear algebra.}
\resumeItemListEnd
\vspace{-15pt}

\resumeProjectHeading
{\textbf{Mathematics Training and Talent Search (MTTS)} $|$
\emph{Level 0 Summer Camp}}{May 2020 -- June 2020}
\resumeItemListStart
\resumeItem{Gained a deeper understanding of topics including logic,
sequence and series, vector spaces.}
\resumeItem{The programme promoted active discussions in mathematics
and gave a platform to connect with people passionate about mathematics.}
\resumeItemListEnd
\vspace{-15pt}

\resumeSubHeadingListEnd
\vspace{-5pt}

\section{Reading Groups}
\resumeSubHeadingListStart

\resumeSubheading{Community for Linear Algebra Pursuits}{November
2023 -- December 2023}{Reading
Group}{\href{https://www.neeldhara.com}{Dr. Neeldhara Misra}, IIT
Gandhinagar}
% \vspace{-15pt}
\resumeItemListStart
\resumeItem{Reading group for the book \textit{Thirty-three
Miniatures: Mathematical and Algorithmic Applications of Linear Algebra}}
\resumeItem{{\href{https://linearalgebra33.discourse.group/}{Access
the community website here}}}
\resumeItemListEnd

\resumeSubheading{Operator Algebra Reading Group}{October 2023 --
February 2024}{}{}
\vspace{-18pt}
\resumeItemListStart
\resumeItem{Reading group of graduate students interested in operator
algebras and related topics.}
\resumeItem{{\href{https://sites.google.com/view/operator-algebras/}{Access
the website here}}}
\resumeItemListEnd

\pagebreak

\resumeSubheading{Computability}{Jananuary 2022 -- March
2022}{Student Reading Project}{Ashish Kujur, IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{Learned about computable functions in unlimitied register
machines(URM).}
\resumeItem{Reference: \textit{Computability: An Introduction to
Recursive Function Theory}, Nigel Cutland.}
\resumeItem{An article we authored as part of the project was
  published in the quarterly newsletter of Club of Mathematics.
  \href{https://raw.githubusercontent.com/joelsleeba/URM-Computability/master/Computable_Numbers.pdf}{Access
it here}}
\resumeItemListEnd

\resumeSubheading{Students' Recreational MTTS}{June 2020 -- August
2020}{Student Reading Group}{MTTS 2020 Summer Camp Alumni}
\resumeItemListStart
\resumeItem{Reading group aimed to self learn and discuss topics from
\textit{Linear Algebra} by \textit{Friedberg, Incel, Spence}.}
\resumeItem{\href{https://www.notion.so/Students-Recreational-MTTS-83d30db273f74fa08fabebf7163ad843}{Access
the website here}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Additional Courses}
\resumeSubHeadingListStart

\resumeSubheading
{\textbf CS101.2x: Object-Oriented Programming}{July 2020 -- Dec. 2020}
{Grade: A+}{MOOCs Course, IITBombayX}

\resumeSubheading
{\textbf CS101.1x: Programming Basics}{July 2020 -- Dec. 2020}
{Grade: A+}{MOOCs Course, IITBombayX}

\resumeSubHeadingListEnd

\section{Extracurricular}
\resumeSubHeadingListStart

\resumeSubheading{\TeX - Click}{Dec. 2023}{Firefox Addon}{}
\resumeItemListStart
\resumeItem{Currently developing a Firefox addon to easily extract
  \TeX \ from the equations on websites including arXiv, Wikipedia, and
  StackExchange.
  \href{https://addons.mozilla.org/en-US/firefox/addon/tex-click/}{Access
the addon}}
\resumeItemListEnd

\resumeSubheading{Introduction to C* algebras}{October 9,
2023}{Student Seminar Presentation}{IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{\href{https://github.com/joelsleeba/presentations/blob/master/IISERTVM-C-Algebra/pres.pdf}{Access
the presentation slides}}
\resumeItemListEnd

\resumeSubheading{Math Modelling}{Sept. 2022 -- Nov.
2022}{Volunteer}{The International Genetically Engineered Machine
competition (iGEM), IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{Modelled the partial differential equations for the
  internalization of vesicles through cell membrane.
\href{https://2022.igem.wiki/iiser-tvm/model}{[Link]}}
\resumeItemListEnd

\resumeSubheading{Web Development}{Sept. 2022 -- Nov.
2022}{Volunteer}{The International Genetically Engineered Machine
competition (iGEM), IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{\href{https://2022.igem.wiki/iiser-tvm}{Access the webpage}}
\resumeItemListEnd

\resumeSubheading{Peer Discussion: Real Analysis}{March 31,
2022}{Host}{Club of Mathematics, IISER Thiruvananthapuram}
\resumeItemListStart
\resumeItem{Co-hosted the peer discussion session for first year
integrated BS-MS students.}
% \resumeItem{Framed questions and hosted rounds in the online quiz
% competition.}
\resumeItemListEnd

% \resumeSubheading{Pi Quiz 3.0}{March 14, 2022}{Host}{Club of
% Mathematics, IISER Thiruvananthapuram}

% \resumeSubheading{XOR Encryptor}{Jan.
% 2022}{Developer}{\href{https://github.com/joelsleeba/xor-encryptor}{Repository}}

\resumeSubheading{Online Foundation Course in Mathematics}{September
2021 -- October 2021}{Mentor}{MTTS Trust}
\resumeItemListStart
\resumeItem{Guided first and second year undergraduate students in
the post lecture discussion sessions of the course.}
\resumeItem{The course aimed at helping students develop mathematical
thinking by focusing on logic, sequence and limits and linear algebra.}
\resumeItemListEnd

% \resumeSubheading{CSSart}{May.
% 2020}{Developer}{\href{https://joelsleeba.github.io/CSSart}{Website}}
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart

\resumeSubheading
{\textbf CSIR National Eligibility test for Junior Research
Fellowship}{June 2024}
{Rank 58 (out of 29118 applicants), Mathematics}{National Testing
Agency, India}

\resumeSubheading
{\textbf Graduate Aptitude Test in Engineering}{February 2024}
{Rank 127 (out of 13425 applicants), Mathematics}{India}

\resumeSubheading
{\textbf M.Sc Entrance Examination}{2021}
{Rank 1, Mathematics}{Pondicherry University}

\resumeSubheading
{\textbf M.Sc Entrance Examination}{2021}
{Rank 3, Mathematics}{Hyderabad Central University}

\resumeSubHeadingListEnd

% \section{Volunteering and Other Projects}
%     \resumeSubHeadingListStart
%
%             % \resumeItemListStart
%             %     \resumeItem{Developed a simple programme to
% encrypt text and files using a symmetric key or password.
% \href{https://github.com/joelsleeba/xor-encryptor}{[Link]}}
%             % \resumeItemListEnd
%
%         \resumeSubheading{CSSart}{May.
% 2020}{Developer}{\href{https://joelsleeba.github.io/CSSart}{Website}}
%             % \resumeItemListStart
%             %     \resumeItem{Created a handful of webpages as a
% part of learning CSS. \href{https://joelsleeba.github.io/CSSart}{[Link]}}
%             % \resumeItemListEnd
%
%
%         %     \resumeItemListStart
%         %         \resumeItem{Contributed to the SETI@Home
% initiative which uses idle time in computational device for data
% crunching throught the BOINC platform.}
%         %     \resumeItemListEnd
%
%     \resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
      \textbf{Programming}{: Python, C, C++, Java, Bash, SQL} \\
      \textbf{Markup}{: \LaTeX, MarkDown, HTML, CSS} \\
      \textbf{CAS}{: MATLAB, GNU Octave, Maxima, SageMath}
    }
\end{itemize}
\vspace{-16pt}

\end{document}
